---
title: "Analysis of Combinatorial Optimization"
output: html_notebook
---
```{r}
comparison_data = read.csv('../data/small_problem_data_1_30_8.csv')

distribution_pairs = c("(0,0)", "(0,1)", "(1,0)", "(1,1)", "(2,0)", "(2,1)")

```

##Distribution Pair (0,0)

Optimal Cost: 0.2781962
```{r}
# Run on the (0, 0) distribution pair.
comparison_data_0_0 = comparison_data[c(1:30), c(5,7,9)]

anneal_diff = comparison_data_0_0$anneal_cost - comparison_data_0_0$opt_cost
xentropy_diff = comparison_data_0_0$xentropy_cost - comparison_data_0_0$opt_cost

t.test(anneal_diff)
t.test(xentropy_diff)
```

## Distribution Pair (0,1)

Optimal Cost: 0.4561246
```{r}
# Run on the (0, 1) distribution pair.
comparison_data_0_1 = comparison_data[c(31:60), c(5,7,9)]

anneal_diff = comparison_data_0_1$anneal_cost - comparison_data_0_1$opt_cost
xentropy_diff = comparison_data_0_1$xentropy_cost - comparison_data_0_1$opt_cost

t.test(anneal_diff)
t.test(xentropy_diff)
```
The results for the t-test between the simulated annealing and brute force method is not coming out correctly because they have the same cost.

## Distribution Pair (1,0)

Optimal Cost: 0.05225641
```{r}
# Run on the (1, 0) distribution pair.
comparison_data_1_0 = comparison_data[c(61:90), c(5,7,9)]

anneal_diff = comparison_data_1_0$anneal_cost - comparison_data_1_0$opt_cost
xentropy_diff = comparison_data_1_0$xentropy_cost - comparison_data_1_0$opt_cost

t.test(anneal_diff)
t.test(xentropy_diff)
```

## Distribution Pair (1,1)

Optimal Cost: 0.7521175
```{r}
# Run on the (1, 1) distribution pair.
comparison_data_1_1 = comparison_data[c(91:120), c(5,7,9)]

anneal_diff = comparison_data_1_1$anneal_cost - comparison_data_1_1$opt_cost
xentropy_diff = comparison_data_1_1$xentropy_cost - comparison_data_1_1$opt_cost

t.test(anneal_diff)
t.test(xentropy_diff)
```

## Distribution Pair (2,0)

Optimal Cost: 0.3328103
```{r}
# Run on the (2, 0) distribution pair.
comparison_data_2_0 = comparison_data[c(121:150), c(5,7,9)]

anneal_diff = comparison_data_2_0$anneal_cost - comparison_data_2_0$opt_cost
xentropy_diff = comparison_data_2_0$xentropy_cost - comparison_data_2_0$opt_cost

t.test(anneal_diff)
t.test(xentropy_diff)
```
The results for the t-test between the simulated annealing and brute force method is not coming out correctly because they have the same cost.

## Distribution Pair (2,1)

Optimal Cost: 0.1326781
```{r}
# Run on the (2, 1) distribution pair.
comparison_data_2_1 = comparison_data[c(151:180), c(5,7,9)]

anneal_diff = comparison_data_2_1$anneal_cost - comparison_data_2_1$opt_cost
xentropy_diff = comparison_data_2_1$xentropy_cost - comparison_data_2_1$opt_cost

t.test(anneal_diff)
t.test(xentropy_diff)
```


